More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-11-23 2016-Weak-FH-Bisim/WeakBisim.tex

\begin{definition}[pLTS]
\label{pLTS}
A pLTS is a tuple
$pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
\begin{itemize}
\item[$\bullet$]
$S$ is a set of states.
\item[$\bullet$]
$s_0 \in S$ is the initial state.
%\item[$\bullet$]
 %Variables in
%$\iv(\alpha)$ are assigned by the action, other variables can be assigned
%by the additional assignments.
\item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
$L$ is the set of labels of the form
$\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
\AlgB$ is a guard, and the variables $x_j\in P$
are assigned the expressions $e_j\in \AlgE$.
If 
$s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
		$\vars(e_b)\!\subseteq\! \vars(s')$, and
		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.

@@

\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

@@

\begin{definition}[Open automaton]
	\label{def:open-automaton}
	An \emph{open automaton} is a structure\\ $A =
	<LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
	\begin{itemize}
		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
		\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
		among $\mathcal{S}$,
		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
		$t\in \mathcal{T}$ there exist $I'$, $J'$ with $I'\subseteq I$, $J'
		\subseteq J$, such that $t$ is an open transition over $LTS_i^{i\in I'}$, $J'$,
		and  $\mathcal{S}$.

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\ SV\!\!= \!{\tt clone}(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
    \alpha'_k \\
    	Leaves(p) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\in I_k.
    	\pNet_m \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}
    	%\land
    	%Leaves(\pNet_m) = \overline{pLTS}^{L_k})
    	\\
    	I' = \biguplus_{m\in I_k}\!\! I_m'
    	\\ J' = \biguplus_{m\in I_k}\!\! J'_m \uplus J_k 	\\
    	\Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
    	\forall j\!\!\in\!\! J_k. {\tt 
    		fresh}(b_j) \\ {\tt fresh}(v) \\ 
    	\forall i\in
    	L\backslash I'.\,s'_i=s_i 
    }
    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $

@@

Let \ERIC{$\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$} be a relation over the set $\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate
More precisely, for any pair $(s^1,s^2)$, there is a 
   single
      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related 
      if $\Pred_{s^1,s^2}$ 
      is 
      true, i.e. the states are related when the variables in $s^1$ and $s^2$ verify the 
      predicate $\Pred_{s^1,s^2}$.

@@

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <L_1,J,\mathcal{S}_1, s_0,
   \mathcal{T}_1>$ and $A_2 = <L_2,J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
   are open automata where the set
   of holes are equal %\LUDO{added:} 
   and of the same sort.  %\LUDO{changed:}

 Then 
$\mathcal{R}$ is an FH-bisimulation iff for any  states
$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred)\in\mathcal{R}$, we 
have
the following:
\end{minipage}
\hspace{2mm}
\begin{minipage}{0.30\linewidth}
	\includegraphics[width=\linewidth]{XFIG/Bisim}
\end{minipage}

@@

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
    \inferrule*[myfraction=\reddottedrule]
         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{2 x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {v_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J_1=J_{2x}, (s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

@@

\begin{definition}[Weak open transitions]
  Let $A = <L,J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton.
  We define $\mathcal{T^*}$ the \emph{Weak open transition relation}
  with respect to a set of invisible actions $\mathcal{Inv}$ as:

 \begin{mathpar}
 \inferrule*[myfraction=\reddottedrule]
         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, 
           \{\xrightarrow{b_j}_j\}^{j\in J},\Pred,\Post}
         {s \OTWeakarrow {v} s'}
         \in \mathcal{T}^*
 \end{mathpar}

@@

 \TODO{Pas si simple !!!}

@@

\noindent
Let $A_1$ and $A_2$ be open automata, and $\mathcal{R}$ a relation over
$S_1$ and $S_2$, as in Definition \ref{def-FH-bisim}.

Then 
   $\mathcal{R}$ is an Weak FH-bisimulation iff for any  states
$s\in\mathcal{S}_1$ and\\
$t\in\mathcal{S}_2$, $(s,t|\Pred)\in\mathcal{R}$, we 
   have the following:

@@

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2^*$:
 \begin{mathpar}
    \inferrule*[myfraction=\reddottedrule]
         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{2 x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {v_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{2x}, (s',t_x|\Pred_{s^{1'},t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

@@

       \section{Proofs of basic properties on pNets}
       \subsection{Equivalence relation (Theorem~\ref{thm-equiv})}
        \emph{Suppose $\mathcal{R}$ 
       	is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, 
       	$\mathcal{R}$ is 
       	reflexive, symmetric and transitive.
       	}
%%% A PROOF WITH CONSTRUCTIVE AERGUMENTS BUT THAT DOES NOT WORK

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{t_{p i}\xrightarrow{a_{p i x}}_i t_{p i x}\}^{i\in I_{2 p x}},
       		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{t_p \OTarrow {v_{px}} t_{p x}}
       	%         \right)
       	\end{mathpar}

       	such that  $\forall x, J_1=J_{2px}, (s',t_{px}|\Pred_{{px}})\in 
       	\mathcal{R}$;
       	and  \\

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{u_i\xrightarrow{a_{i p x y}}_i u_{i p x y}\}^{i\in I_{3 p x y}},
       		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTarrow {v_{pxy}} u_{pxy}}
       	%         \right)

       	\end{mathpar}
       	such that  $\forall y, J_{2px}=J_{3pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_p \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land v_{px}\!=\!v_{pxy} \land
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.

@@

       	First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
       	({s}',s_{pxy}|\Pred\,'_{{pxy}})\in \mathcal{R}''$. 
       	Indeed for any 
       	$p$, 
       	$x$, and 
       	$y$, $t_{px}$
       	relate ${s}'$ and $u_{pxy}$, indeed
       	$(s',t_{px}|\Pred_{{px}})\in \mathcal{R}$
       	and $(t_{px},u_{pxy}|\Pred{{pxy}})\in \mathcal{R}'$. 
       	More precisely, $t_{px} \in ({t_p}')^{p\in P'}$ where $({t_p}')^{p\in 
       		P'}$ 
       	is 
       	the set of states relating ${s}'$ and $u_{pxy}$.
       	Consequently, for all $p$, $x$, $y$, $\Pred_{px}\land 
       	\Pred_{{pxy}}\implies 
       	\Pred\,'_{{pxy}}$ (this is one element of the  disjunction defining the 
       	predicate 
       	relating ${s}'$ and $u_{pxy}$ in the definition of $\mathcal{R}''$).

@@

       	Second, we need \\
       	\begin{small}
       		$\Pred\,'' \land \Pred_{OT}\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
       		\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v\!=\!v_{pxy} \land
       		\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
       	\end{small}

       	We have, for all $p$
       	\begin{small}
       		$\Pred_p \land \Pred_{OT}\land\Pred'_p\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred'_p\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred'_p)
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\big( \forall j. b_j=b_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
       		\big( \forall j'. b_{j'px}=b_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
       		\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
       		\Rightarrow \big( 
       		\Pred_{OT_{pxy}}
       		\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
       		\land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
       		$

@@

By construction, the Post substitutions only have an effect on the  
variables of the open automaton they belong to, they also produce terms containing only 
variables of the open automaton they belong to. Finally, because of the domain of the 
substitutions  and of the predicates, we have:\\
       	$\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	= 
       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
       	\Pred_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	= \Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $

>>>>

\begin{definition}[pLTS]
\label{pLTS}
A pLTS is a tuple
$\pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
\begin{itemize}
\item[$\bullet$]
$S$ is a set of states.
\item[$\bullet$]
$s_0 \in S$ is the initial state.
%\item[$\bullet$]
 %Variables in
%$\iv(\alpha)$ are assigned by the action, other variables can be assigned
%by the additional assignments.
\item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
$L$ is the set of labels of the form
$\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
\AlgB$ is a guard, and the variables $x_j\in P$
are assigned the expressions $e_j\in \AlgE$.
If 
$s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
		$\vars(e_b)\!\subseteq\! \vars(s')$, and
		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.

@@

\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

@@

\begin{definition}[Open automaton]
	\label{def:open-automaton}
	An \emph{open automaton} is a structure\\ $A =
	<\LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
	\begin{itemize}
		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
		\item[$\bullet$]  $\LTS_i^{i\in I}$ is a family of LTSs,
		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
		among $\mathcal{S}$,
		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
		$t\in \mathcal{T}$ there exist $I'$, $J'$ with $I'\subseteq I$, $J'
		\subseteq J$, such that $t$ is an open transition over $\LTS_i^{i\in I'}$, $J'$,
		and  $\mathcal{S}$.

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\ SV\!\!= \!{\tt clone}(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
    \alpha'_k \\
    	Leaves(p) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\in I_k.
    	\pNet_m \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}
    	%\land
    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})
    	\\
    	I' = \biguplus_{m\in I_k}\!\! I_m'
    	\\ J' = \biguplus_{m\in I_k}\!\! J'_m \uplus J_k 	\\
    	\Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
    	\forall j\!\!\in\!\! J_k. {\tt 
    		fresh}(b_j) \\ {\tt fresh}(v) \\ 
    	\forall i\in
    	L\backslash I'.\,s'_i=s_i 
    }
    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $

@@

Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
$\mathcal{S}_2$ constrained by a predicate
More precisely, for any pair $(s,t)$, there is a 
   single
      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
      if $\Pred_{s,t}$ 
      is 
      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
      predicate $\Pred_{s,t}$.

@@

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <\overline{\LTS_1},J,\mathcal{S}_1, s_0,
   \mathcal{T}_1>$ and $A_2 = <\overline{\LTS_2},J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
   are open automata where the set
   of holes are equal %\LUDO{added:} 
   and of the same sort.  %\LUDO{changed:}

 Then 
$\mathcal{R}$ is an FH-bisimulation iff for any  states
$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred)\in\mathcal{R}$, we 
have
the following:
\end{minipage}
\hspace{2mm}
\begin{minipage}{0.30\linewidth}
	\includegraphics[width=\linewidth]{XFIG/Bisim}
	\TODO{change fig: s1,s2 $\to$ s,t}
\end{minipage}

@@

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
    \inferrule*[myfraction=\reddottedrule]
         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{ x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {v_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

@@

\begin{definition}[Weak open transitions]
  Let $A = <\overline{\LTS},J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton.
  We define $\mathcal{T^*}$ the \emph{weak open transition relation}
  with respect to a set of invisible actions $\mathcal{I}$ as:

 \begin{mathpar}
 \inferrule*[myfraction=\reddottedrule]
         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, 
           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred,\Post}
         {s \OTWeakarrow {v} s'}
         \in \mathcal{T}^*
 \end{mathpar}

@@

 \TODO{Pas si simple !!!!!!!!!!!!!!!!!!!}

@@

\noindent
Let $A_1$ and $A_2$ be open automata, and $\mathcal{R}$ a relation over
$\mathcal{S}_1$ and $\mathcal{S}_2$, as in Definition \ref{def-FH-bisim}.

Then 
   $\mathcal{R}$ is a weak FH-bisimulation iff for any  states
$s\in\mathcal{S}_1$ and\\
$t\in\mathcal{S}_2$, $(s,t|\Pred)\in\mathcal{R}$, we 
   have the following:

@@

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2^*$:
 \begin{mathpar}
    \inferrule*[myfraction=\reddottedrule]
         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {v_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

@@

       \section{Proofs of basic properties on pNets}
       \subsection{Equivalence relation (Theorem~\ref{thm-equiv})}
        \emph{Suppose $\mathcal{R}$ 
       	is an FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, 
       	$\mathcal{R}$ is 
       	reflexive, symmetric and transitive.
       	}
%%% A PROOF WITH CONSTRUCTIVE AERGUMENTS BUT THAT DOES NOT WORK

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{t_{p i}\xrightarrow{a_{p i x}}_i t_{p i x}\}^{i\in I_{p x}},
       		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{t_p \OTarrow {v_{px}} t_{p x}}
       	%         \right)
       	\end{mathpar}

       	such that  $\forall x, J_1=J_{px}, (s',t_{px}|\Pred_{{px}})\in 
       	\mathcal{R}$;
       	and  \\

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{u_i\xrightarrow{a_{i p x y}}_i u_{i p x y}\}^{i\in I_{p x y}},
       		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTarrow {v_{pxy}} u_{pxy}}
       	%         \right)

       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_p \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land v_{px}\!=\!v_{pxy} \land
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.

@@

       	First, $\forall y, \forall x, \forall p, J_1=J_{px}=J_{pxy}, 
       	({s}',u_{pxy}|\Pred\,'_{{pxy}})\in \mathcal{R}''$. 
       	Indeed for any 
       	$p$, 
       	$x$, and 
       	$y$, $t_{px}$
       	relate ${s}'$ and $u_{pxy}$, indeed
       	$(s',t_{px}|\Pred_{{px}})\in \mathcal{R}$
       	and $(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$. 
       	More precisely, $t_{px} \in ({t_p}')^{p\in P'}$ where $({t_p}')^{p\in 
       		P'}$ 
       	is 
       	the set of states relating ${s}'$ and $u_{pxy}$.
       	Consequently, for all $p$, $x$, $y$, $\Pred_{px}\land 
       	\Pred_{{pxy}}\implies 
       	\Pred\,'_{{pxy}}$ (this is one element of the  disjunction defining the 
       	predicate 
       	relating ${s}'$ and $u_{pxy}$ in the definition of $\mathcal{R}''$).

@@

       	Second, by definition of bisimulation we need (recall that $\Pred\,''$ is the 
       	original predicate relating $s$ and $u$ by definition of the transitive 
       	closure):\\
       	\begin{small}
       		$\Pred\,'' \land \Pred_{OT}\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
       		\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v\!=\!v_{pxy} \land
       		\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
       	\end{small}

       	We have, for all $p$
       	\begin{small}
       		$\Pred_p \land \Pred_{OT}\land\Pred_p\!'\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred_p\!'\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred_p\!')
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\big( \forall j. b_j=b_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
       		\big( \forall j'. b_{j'px}=b_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
       		\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
       		\Rightarrow \big( 
       		\Pred_{OT_{pxy}}
       		\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
       		\land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
       		$

@@

By construction, the Post substitutions only have an effect on the  
variables of the open automaton they belong to, they also produce terms containing only 
variables of the open automaton they belong to. Finally, because of the domain of the 
substitutions  and of the predicates, we have:\\
       	$\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	= 
       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
       	\Pred_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	= \Pred\!'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $
